VULCAN Analysis Combined

### 2018-02-05 ChIP-seq_GRHL2/Manuscript_Figures.Rmd
Update Readme

interect<-intersect(rownames(vobj_results$metabric$mrs), 
                       rownames(vobj_results$tcga$mrs))
plot(-log10(vobj_results$metabric$mrs[interect,"pvalue"]),
     -log10(vobj_results$tcga$mrs[interect,"pvalue"]),
     pch=20, xlab="Metabric Network Enrichment Score", ylab="TCGA Network Enrichment Score",main="VULCAN analysis of GRHL2 ChIP-Seq")

filtered<-(log10(vobj_results$metabric$mrs[interect,"pvalue"])^2+log10(vobj_results$tcga$mrs[interect,"pvalue"])^2)>2

text(-log10(vobj_results$metabric$mrs[interect,"pvalue"][filtered]),
     -log10(vobj_results$tcga$mrs[interect,"pvalue"][filtered])-0.1,
     labels=interect[filtered])

points(-log10(vobj_results$metabric$mrs[interect,"pvalue"][c("GATA3","PGR","FOXA1","ESR1","GRHL2")]),
       -log10(vobj_results$tcga$mrs[interect,"pvalue"][c("GATA3","PGR","FOXA1","ESR1","GRHL2")]),pch=20,col="red")
text(-log10(vobj_results$metabric$mrs[interect,"pvalue"][c("GATA3","PGR","FOXA1","ESR1","GRHL2")]),
     -log10(vobj_results$tcga$mrs[interect,"pvalue"][c("GATA3","PGR","FOXA1","ESR1","GRHL2")])-0.1,col="red",
     labels=c("GATA3","PGR","FOXA1","ESR1","GRHL2"))
```

>>>>

interect<-intersect(rownames(vobj_results$metabric$mrs), 
                       rownames(vobj_results$tcga$mrs))
plot(-log10(vobj_results$metabric$mrs[interect,"pvalue"]),
     -log10(vobj_results$tcga$mrs[interect,"pvalue"]),
     pch=20, xlab="Metabric Network Enrichment Score", ylab="TCGA Network Enrichment Score",main="VULCAN analysis of GRHL2 ChIP-Seq",
     col="gray"
     )

filtered<-(log10(vobj_results$metabric$mrs[interect,"pvalue"])^2+log10(vobj_results$tcga$mrs[interect,"pvalue"])^2)>3
filtered[c("GATA3","PGR","FOXA1","ESR1","GRHL2")]<-rep(FALSE,5)

points(-log10(vobj_results$metabric$mrs[interect,"pvalue"][filtered]),
     -log10(vobj_results$tcga$mrs[interect,"pvalue"][filtered]),
     labels=interect[filtered],cex=1)

text(-log10(vobj_results$metabric$mrs[interect,"pvalue"][filtered]),
     -log10(vobj_results$tcga$mrs[interect,"pvalue"][filtered])-0.1,
     labels=interect[filtered],cex=1)

points(-log10(vobj_results$metabric$mrs[interect,"pvalue"][c("GATA3","PGR","FOXA1","ESR1","GRHL2")]),
       -log10(vobj_results$tcga$mrs[interect,"pvalue"][c("GATA3","PGR","FOXA1","ESR1","GRHL2")]),pch=20,col="red",cex=1.5)
text(-log10(vobj_results$metabric$mrs[interect,"pvalue"][c("FOXA1","ESR1","GRHL2")]),
     -log10(vobj_results$tcga$mrs[interect,"pvalue"][c("FOXA1","ESR1","GRHL2")])+0.2,col="red",
     labels=c("FOXA1","ESR1","GRHL2"),cex=1.25,font=2)
text(-log10(vobj_results$metabric$mrs[interect,"pvalue"][c("GATA3","PGR")])+0.2,
     -log10(vobj_results$tcga$mrs[interect,"pvalue"][c("GATA3","PGR")]),col="red",
     labels=c("GATA3","PGR"),cex=1.25,font=2)
```

### 2018-02-05 Manuscript_Figures_Combined.Rmd
Update Readme

---
title: "VULCAN Analysis Combined"
author: "Andrew Holding"
date: "1/22/2018"
output:
  pdf_document:
    fig_caption: yes
    fig_height: 8
    fig_width: 8
    highlight: tango
    number_sections: yes
    toc: yes
    toc_depth: 3
  html_document:
    fig_caption: yes
    fig_height: 8
    fig_width: 8
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 3
always_allow_html: yes
---

@@

>>>>

---
title: "VULCAN Analysis Combined"
author: "Andrew Holding"
date: "1/22/2018"
output:
  html_document:
    fig_caption: yes
    fig_height: 8
    fig_width: 8
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 3
  pdf_document:
    fig_caption: yes
    fig_height: 8
    fig_width: 8
    highlight: tango
    number_sections: yes
    toc: yes
    toc_depth: 3
always_allow_html: yes
---

@@

#GRHL2 qPLEX-RIME Analysis
```{r GRHL2 eRNA, child = 'eRNA/plot_eRNA.Rmd'}
```
